### 2019-03-02 manuscript/discussion.tex
- addition of a promised diploidization justification and fodder for discussion - requisite references - fixed spilled text on pathways table

% where WGD is in Solanaceae--motivation and delta rate analyses
% diploidization: comment
%     effect on inferred diversification

>>>>

% where WGD is in Solanaceae--motivation and delta rate analyses
% diploidization: comment
Diploidization needs to be considered in diversification models because higher rates of net diversification (speciation minus extinction) in diploids can be obtained from models that ignore the possibility of a polyploid lineage that has diploidized being the diversification enhancer. Hence, in a diploidization lacking model, diploids will show higher rates of diversification when in fact it is a polyploidy event and its subsequent diploidization that generated higher speciation and less extinction.  By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with stochastic models.

% B: This is my pitch for motivation of the \delta paragraph and/or wording for how to reconcile estimates and genomic data (providing summary of data--to date)
Diploidization is widely considered to be relatively rare, compared with polyploidization, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history.
As a consequence, it is possible that nearly all extant species classified as ``diploid" in our analyses are possibly secondary diploids, having undergone both polyploidization and re-diploidization.
Genomic evidence indicates that such an event may have occurred prior to the origin of the family Solanaceae. 
\citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \textit{Solanum lycopersicum}, may have experienced one or more paleopolyploid events.
A subsequent analysis of synteny between grape and \textit{Solanum} genomes, as well as the distribution between inferred paralogs within \textit{Solanum} (tomato and potato) genomes both suggest that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances, is approximately 71 million years \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently re-diploidized, because common base chromosome numbers this and related families are n=11-12. 
%Not unlikely, because Arabidopsis n=5.
On the other hand, studies comparing map-based genome synteny within the family find no evidence for recent polyploidization-diploidization \citep{wu_2010a}. 
Simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species, including all of those in the relatively cytogenetically conserved `x=12' group, which includes tomato, potato, eggplant, pepper, and tobacco.
%B: Once this is re-arranged, and made to fit with the rest of the discussion, add what this has to do with re-diploidization and how to interpret $\delta$.

%     effect on inferred diversification
